Difference Scores: Paired Samples T-test

### 2024-03-06 examples/_1a_Examples_DifferenceScores_PairedTtests.qmd
updates

>>>>

----

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive

# Specify the file ID and the destination path
file_id <- "1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr" # Replace with your actual file ID
dest_file <- "my_data.rds" # Specify your destination path

# Download the file
drive_download(as_id(file_id), path = dest_file, overwrite = TRUE)

# Load the .rds file for analysis
my_data <- readRDS(dest_file)

# Begin your analysis (example: view the first few rows)
head(my_data)

----

### 2024-03-06 examples/data_shift_code.qmd
updates

# Define event names to be retained in the analysis and convert variables to appropriate data types
eventnames_to_include <- c("baseline_year_1_arm_1",
                           "1_year_follow_up_y_arm_1",
                           "2_year_follow_up_y_arm_1",
                           "3_year_follow_up_y_arm_1",
                           "4_year_follow_up_y_arm_1")

df <- merged_data %>%
  filter(eventname %in% eventnames_to_include) %>%
  mutate(
    src_subject_id = as.factor(src_subject_id),
    eventname = factor(eventname, levels = eventnames_to_include, ordered = TRUE),
    age = as.numeric(age),
    sex = as.factor(sex),
    race.4level = as.factor(race.4level),
    hisp = as.factor(hisp),
    high.educ.bl = as.factor(high.educ.bl),
    household.income.bl = as.factor(household.income.bl),
    acs_raked_propensity_score = as.numeric(acs_raked_propensity_score),
    rel_family_id.bl = as.factor(rel_family_id.bl),
    site_id_l = as.factor(site_id_l),
    nihtbx_totalcomp_fc = as.numeric(nihtbx_totalcomp_fc),
    anthroweightcalc = as.numeric(anthroweightcalc),
    anthroweightcalc = as.numeric(anthroweightcalc)
  ) %>%
  # Exclude cases from unused assessment waves
  filter(!is.na(eventname))
```

@@

```{r}

Randomly drawn subsample
# Assuming your dataframe is named df

@@

# Calculate the number of rows to sample (30% of the dataset)
sample_size <- floor(0.3 * nrow(df))

@@

# Subset the dataframe using the sampled indices
df_sampled <- df[sampled_indices, ]

@@

```{r}
# Generating random/unique participant IDs
set.seed(123) # For reproducibility
# Create a vector of random unique IDs
new_ids <- sample(10000:99999, size = nrow(df_sampled), replace = FALSE)

# Assign the new IDs to the participant_id column or to a new column
df_sampled$new_participant_id <- new_ids

# Optionally, if you want to replace the original ID column:
df_sampled$participant_id <- df_sampled$new_participant_id

@@

>>>>

# Define event names to be retained in the analysis and convert variables to appropriate data types
eventnames_to_include <- c(
    "baseline_year_1_arm_1",
    "1_year_follow_up_y_arm_1",
    "2_year_follow_up_y_arm_1",
    "3_year_follow_up_y_arm_1",
    "4_year_follow_up_y_arm_1"
)

df_temp1 <- merged_data %>%
    filter(eventname %in% eventnames_to_include) %>%
    mutate(
        src_subject_id = as.factor(src_subject_id),
        eventname = factor(eventname, levels = eventnames_to_include, ordered = TRUE),
        age = as.numeric(age),
        sex = as.factor(sex),
        race.4level = as.factor(race.4level),
        hisp = as.factor(hisp),
        high.educ.bl = as.factor(high.educ.bl),
        household.income.bl = as.factor(household.income.bl),
        acs_raked_propensity_score = as.numeric(acs_raked_propensity_score),
        site_id_l = as.factor(site_id_l),
        nihtbx_totalcomp_fc = as.numeric(nihtbx_totalcomp_fc),
        anthroweightcalc = as.numeric(anthroweightcalc),
        anthroweightcalc = as.numeric(anthroweightcalc)
    ) %>%
    # Exclude cases from unused assessment waves
    filter(!is.na(eventname))
```

@@

```{r}
# Creating a randomly drawn subsample
df_sampled_temp <- df_temp1

@@

# Calculate the number of rows to sample (30% of the dataset)
sample_size <- floor(0.3 * nrow(df_sampled_temp))

@@

# Subset the dataframe using the sampled indices
df_sampled <- df_sampled_temp[sampled_indices, ]

@@

```{r}
# Generating random/unique participant IDs
set.seed(123) # For reproducibility

# Create a vector of random unique IDs and directly replace the original ID column
df_sampled$src_subject_id <- sample(10000:99999, size = nrow(df_sampled), replace = FALSE)

df <- df_sampled

# Save df in the current working directory as my_dataframe.rds
saveRDS(df, "FaKEbcd.rds")

@@

```{r}
# Install and load the googledrive package
if (!requireNamespace("googledrive", quietly = TRUE)) install.packages("googledrive")
library(googledrive)

# Authenticate with Google Drive

# Specify the file ID and the destination path
file_id <- "1_gnaEx0wJ28tT0CD_B6mPFwngdfSb6Dr" # Replace with your actual file ID
dest_file <- "my_data.rds" # Specify your destination path

# Download the file
drive_download(as_id(file_id), path = dest_file, overwrite = TRUE)

# Load the .rds file for analysis
my_data <- readRDS(dest_file)

# Begin your analysis (example: view the first few rows)
head(my_data)
